
\chapter{Sprint 4}
\label{Sprint4}
\lhead{Chapter 10. \emph{Sprint 4}}

\section{Goal(s)}

The main goal of this sprint was to finalize and demonstrate a second prototype of the system,
which included: a) the backend, b) the frontend, c) two Android applications.
These had to be ready for October the 24th when our customer planned to visit Trondheim.

\section{Planning}

This sprint's plan consisted in one last development effort to complete the second prototype
before our meeting with our customer and in view of the feature freeze deadline.
For our colleague in Oslo, we planned documentation exclusively in order
not to fall behind with the status of the report.

\section{Duration}
The duration of the sprint was the following:
\begin{itemize}
\item Start: October, 21st
\item End: November, 03rd
\end{itemize}

\section{Backlog}
See below the sprint backlog:
\begin{enumerate}[1.]
\item \textbf{Project management} included:
	\begin{itemize}
		\item \textbf{Weekly startup meeting}
		\item \textbf{Weekly meetings}: 
			meetings with both the customer and the supervisor. internal meeting with our colleague in Oslo.
		\item \textbf{Meeting notes}:
			taking notes during meetings, reviewing of the notes.
		\item \textbf{Status reports}:
			for both week 43 and 44
		\item \textbf{Risk analysis}:
			updated on a weekly basis, so twice per sprint.
		\item \textbf{Planning for the next iteration}:
			prepare a plan for the next iteration
	\end{itemize}
	\item \textbf{System development}
		additional system development to accomodate fixes to the front end.
	\item \textbf{Web application development}
		develop a web application which integrates weight measurements
		on HealthVault in our system.
	\item \textbf{Report work}
		to be done by the team member in Trondheim.
	\item \textbf{Additional report work}
		to be done by the team member in Oslo.
	\item \textbf{Testing}
		produce some tests using an automated test suite.
\end{enumerate}

\section{Results and feedback}

During this sprint we worked mostly on system development, which proceeded smoothly
with one exception. Withings integration with HealthVault, which we planned to use for
our demonstration, was not working as expected: Withings failed to send the data acquired
by the scale device to HealthVault. Unfortunately, after various attempts, we decided
to change the scenario for our demonstration. We couldn't fix the problem
ourselves because we had no control over Withings' system.

A second prototype of the system was completed on schedule before our
planned meeting with the customer, which would have been on the 24th.
However, the customer canceled the meeting and proposed to reschedule it for the 30th.

Considering we had some more time to dedicate to development activities and in view
of the feature freeze deadline (M3) by the end of the sprint, we took initiative
and submitted a new possible application prototype idea to the customer.
It consisted of a web application which would feature HealthVault integration
similarly to the Android application.
The customer expressed his interest in such application because it would have
used a different technology other than Android. He inquired about its feasibility
in such a short amount of time (less than two weeks). We were confident that we
could have re-used some code shipped with HealthVault SDK to minimize the amount
of code we would have had to write ourselves, so we committed its development.

On the 30th of November, very early in the morning the customer sent us a mail
were he canceled our meeting. However, he was available for a Skype meeting.
We were able to demonstrate him our product via Skype, including the last application
prototype which had been developed in one week time. He was very pleased with our work.

\section{Evaluation}

The sprint was very rewarding.
Receiving a good evaluation from the customer proved to be very valuable for the group,
especially because the project was drawing to an end and timing was becoming tight;
there was no time left to make any big adjustments to the product.
The feedback from the customer motivated the group to keep up the good work
and make one big final effort to finish the documentation and prepare a presentation.

Although the scenario for the demonstration had changed and did not include
the Withings scale device, the functionality of the application had not,
so we consider that a very minor issue.

