\chapter{Meeting documents}
\label{AppendixD}
\lhead{Appendix D. \emph{Meeting documents}}

In this appendix we present some documents produced for supervisor meetings.

\iffalse
\section{Overview of advisor meetings}

\begin{table}[H]
\begin{center}
\begin{tabular}{ l | l | l }
  \hline
  Weekday & Date & Meeting Number \\
  \hline\noalign{\smallskip}\noalign{\smallskip}\hline
  Wednesday 	&	21.08.2013 & 1 \\
  	% Was there not a advisor meeting on the first friday or something?
	Monday		&	26.08.2013 & 2 \\
	Monday		& 02.09.2013 & 3 \\
	Monday 		&	09.09.2013 & 4 \\
	Monday 		&	16.09.2013 & 5 \\
	Monday 		&	23.09.2013 & 6 \\
	Monday 		&	30.09.2013 & 7 \\
	Monday 		&	07.10.2013 & 8 \\
	Monday 		&	14.10.2013 & 9 \\
	Monday 		&	21.10.2013 & 10 \\
	Monday 		&	28.10.2013 & 11 \\
	Monday 		&	04.11.2013 & 12 \\
	Monday 		&	11.11.2013 & 13 \\
	Monday 		&	18.11.2013 & 14 \\
  \hline
\end{tabular}
\end{center}
\caption{Customer meetings}
\label{table:customermeetings}
\end{table}
\fi


\section{Weekly status reports}
In this section we present some of the status reports we produced.

\clearpage
% WEEK 35
\subsection{Week 35}

\begin{center}
Weekly status report \#01\\*
Week 35 \\*
Dates 2013-08-26 - 2013-09-01 \\*
TDT4290 Customer Driven Project - Group 17
\end{center}

\textbf{1. Work done}

This week was mostly focused on initial planning of the project.
This included but was not limited to:
\begin{itemize}
\item Internal meeting planning
\item Customer meeting planning
\item Iteration planning
\item Milestone planning
\item Preliminary studies
\end{itemize}


The team agreed the following weekly meetings:
\begin{itemize}
\item On Mondays from 10 to 19
\item On Wednesdays from 15 to 19
\end{itemize}

Each team member agreed to work another 8 hours per week by himself.
The team worked on a preliminary system architecture that was submitted
to the Customer in order to make clear to him our understanding of the project goal.
The Customer was then contacted on Monday the 26th through Skype and provided positive feedback.
The Customer and the team agreed on when to have the next meetings.

A Google Drive folder was created in order to share and collaborate in creating and editing documents. 
The Customer has also access to this folder and has already used it to have a look at the preliminary system architecture.

The team also planned iterations (their number, duration and focus) and milestones for the project
and initiated preliminary studies on relevant technologies.

The team chose a LaTex template for the report.

\textbf{1.1 Meetings}

Monday
from 10 to 19, all members present.
Skype call with the customer, meeting with the supervisor.

Wednesday
from 15 to 19, all members present.

\textbf{2. Plan for next week}

Based on the feedback received from our Customer, we have identified the scope of the project and will conduct studies on relevant technologies in the project’s domain. We will try to identify some formal requirements
for the system, or rather parts of it, based on some use cases and proceed to plan the work for the next iteration.

\textbf{3. Milestones}

Milestones reached: none.

\textbf{4. Problems}

The team is still unsure about the commitment of its fourth member
who still has to show up. Furthermore the timetable for the course
is not clear and inconsistent between sources.

\newpage
% WEEK 36
\subsection{Week 36}

\begin{center}
Weekly status report \#02\\*
Week 36 \\*
Dates 2013-09-02 - 2013-09-08 \\*
TDT4290 Customer Driven Project - Group 17
\end{center}

\textbf{1. Work done}

The team studied relevant existing solutions and technologies.
In particular, among the ones we took into consideration there is an integration platform suggested by the customer himself.

The team set-up the working environments and other tools such as:
\begin{itemize}
\item LaTeX environments for writing the report
\item a server machine for product deployment
\item a git repository managed with GitHub
\item Apache Tomcat web server
\item Android’s SDK
\item IDEs
\end{itemize}

During the Skype meeting, the customer mentioned Microsoft’s  HealthVault and expressed his wish to
see it supported by the integration platform (the product).

The team developed a prototype Android application to monitor the user’s heart rate. An assessment
of the risks for this project was performed and will be updated weekly or once per iteration.

\textbf{1.1 Meetings}

Monday
from 10 to 19, all members present.
Skype call with the customer, meeting with the supervisor.

Wednesday
from 15 to 19, all members present. Emanuele joined two hours late because he had to attend a lecture. 
He had notified the other team members beforehand.

\textbf{2. Plan for next week}

Because team members are not familiar with the technologies involved  additional study is required in order
to decide upon system architecture.
Regarding HealthVault, the team still needs to asses the feasibility of supporting such technology in the product. 
For the next iteration the team will start working on an initial system based on the Spring Framework, the
Apache Tomcat server and database backend.  The team will also start working on the report. 
We will produce more use cases and define requirements.

\textbf{3. Milestones}

Milestones reached: none

\textbf{4. Problems}

The customer is not providing us some documents we requested.
These are not critical for the moment.

\newpage
% WEEK 37
\subsection{Week 37}

\begin{center}
Weekly status report \#03\\*
Week 37 \\*
Dates 2013-09-09 - 2013-09-15 \\*
TDT4290 Customer Driven Project - Group 17
\end{center}

\textbf{1. Work done}

During this week the team has worked toward an initial implementation of the system. 
The database server has been installed and configured on the server machine. The team also started
working on the API itself and on the portal web-page. 
A initial set of requirements for part of the system has been identified. Risk analysis has been updated.

\textbf{1.2 Meetings}

Monday
from 10 to 19, all members present.
Skype call with the customer, meeting with the supervisor.

Wednesday
from 15 to 19, all members present.

\textbf{2. Plan for next week}

Further studies need to be conducted on relevant technologies. 
The team will meet the customer in person on Friday. 
We plan to demonstrate some basic system functionality by then. 
The team should try to get started on the mid-term report as soon as possible.

\textbf{3. Milestones}

Milestones reached: none

\textbf{4. Problems}

Given the size of our group, we expect writing the report will delay our progress with the product itself.





\iffalse

\newpage
% WEEK 38
\subsection{Week 38}

\begin{center}
Weekly status report \#04\\*
Week 38 \\*
Dates 2013-09-16 - 2013-09-22 \\*
TDT4290 Customer Driven Project - Group 17
\end{center}

\textbf{1. Work done}

The team has finished developing a first prototype of the system which has been shown to the customer. 
He provided very positive feedback.
In order to help us plan and prioritize our work we asked the Customer about what he’d like us to start working on next. 
The Customer expressed his interest for HealthVault's integration. 
We informed the Customer that during the next iteration we will mostly focus on report work anyway.

Risk analysis has been updated. Milestones have been reviewed based on supervisor’s advice.

\begin{table}[H]
\begin{center}
\begin{tabular}{ l | l | l }
  \hline
  Activity & Planned & Actual \\
  \hline\noalign{\smallskip}\noalign{\smallskip}\hline
  Studies & 25 & 5 \\
  Project management & 12 & 12 \\
  System developement & 25 & 50 \\
  Application development & 10 & 6 \\
  Database developement & 10 & 2 \\
  Testing & 6 & 4 \\
  Report & 20 & 0 \\
  \hline
\end{tabular}
\end{center}
\caption{Activity chart}
\label{table:activityChartStatusReportWeek38}
\end{table}

\textbf{1.2 Meetings}

Monday from 10 to 19
Emanuele and Sebastian present.
Skype call with the customer, meeting with the supervisor.

Wednesday from 15 to 19
Emanuele and Sebastian present.

Friday from 12.30 to 14.30
Emanuele and Sebastian present, Anders joined on Skype.
Meeting with the Customer in person. Demonstration of the product.

\textbf{2. Plan for next week}

During the next week the team will focus primarily on the report.
We shared our plan for the next iteration with the Customer, as we do regularly. 
Emanuele will also study HealthVault in order to assess the possibility of its integration in our platform. 
Because we are confident we can use HealthVault  we have planned some work for its integration as well.

\textbf{3. Milestones}

M1 First prototype of the system.

\begin{enumerate}
\item An Android application which measures the user’s heart rate and forwards it to the integration platform.
\item A Spring REST endpoint that handles such data and stores it in a local MySQL database.
\item A webpage frontend displaying the data using charts.
\end{enumerate}

Associated deliverables: none


\textbf{4. Problems}

None.


\newpage
% WEEK 39
\subsection{Week 39}

\begin{center}
Weekly status report \#05\\*
Week NN \\*
Dates 2013-09-23 - 2013-09-29 \\*
TDT4290 Customer Driven Project - Group 17
\end{center}

\textbf{1. Work done}

During last week the group has worked exclusively on the report.

\textbf{1.2 Meetings}

Monday from 10 to 19
Emanuele and Sebastian present. Anders joined on Skype.
Meeting with the supervisor. Unable to contact the customer.

Wednesday from 15 to 19
Emanuele and Sebastian present. Anders joined on Skype.


\textbf{2. Plan for next week}

During next week the group will still focus on report work but also spend a little bit of time on development.

\textbf{3. Milestones}

Milestones achieved: None

\textbf{4. Problems}

None.

\fi





\clearpage
\section{Advisor meeting agenda}

See below some of the agendas for our meetings with the advisor.

\subsection{Week 35}

\begin{center}
Agenda for advisor meeting \#01\\*
2013-08-26\\*
\end{center}

\begin{table}[H]
\begin{center}
\begin{tabular}{ l | l }
Time and Data & 2013-08-26 12:00 \\
Place & BU1-108 \\
\end{tabular}
\end{center}
\end{table}

\begin{enumerate}[1.]
\item Approval of agenda
\item Approval of minutes from last advisor meeting. See attached meetings notes.
\item Comments to last weeks minutes
\item Approval of the weekly report. See attached weekly report.
\item Topics to be discussed
\item Progress done last week and plan for the next iteration
\item Other
\item For next meeting
\end{enumerate}

\newpage
\subsection{Week 36}

\begin{center}
Agenda for advisor meeting \#02\\*
2013-09-02\\*
\end{center}

\begin{table}[H]
\begin{center}
\begin{tabular}{ l | l }
Time and Data & 2013-09-02 12:00 \\
Place & BU1-108 \\
\end{tabular}
\end{center}
\end{table}


\begin{enumerate}[1.]
\item Approval of agenda
\item Approval of minutes from last advisor meeting. See attached meetings notes
\item Comments to last weeks minutes
\item Approval of the weekly report. See attached weekly report.
\item Topics to be discussed
\item Progress done last week and plan for the next iteration.
\item Other
\item For next meeting
\end{enumerate}

\clearpage
\section{Advisor meeting notes}

See below some of the notes taken during our meetings with the advisor.

\subsection{Week 45}

\begin{center}
Advisor meeting notes \#X \\
2013-11-04 \\
\end{center}

\begin{table}[H]
\begin{center}
\begin{tabular}{ l | l }
Time and Data & 2013-11-04 14:00 \\
Place & IT building \\
Attendees & Emanuele Di Santo, Sebastian Zalewski \\
Referent & Sebastian Zalewski \\
\end{tabular}
\end{center}
%\caption{Activity chart}
%\label{table:activityChartAdvisorAgenda}
\end{table}

Topics discussed
\begin{enumerate}[1.]
\item The supervisor asks about the meeting with the customer last week. We tell him that the meeting was over skype and not in person. We tell him that the customer was happy. The supervisor asks if the customer asked about a user manual to the application. We tell him that we are going to add it to the report.

\item We ask if it is possible to only let one person present. It can work if only one person talks in the presentation, but the supervisor thinks that all should contribute. It implies that everybody has contributed, if everyone talks. The supervisor tells that it can work if one person talks about the slides, while the other person shows the demonstration. The presentation usually consists of 30 min slides 15 minutes for questions (usually 5-10 minutes questions). Common questions: How we distributed the work, which parts to improve etc… The presentation is the best way to present the work for the censor. The censor might not look thoroughly through the report.

\item The supervisor asks about the status of the report. We tell him that the report is around 100 pages (the main part), the supervisor thinks that is enough
\end{enumerate}

\clearpage
\subsection{Week 46}
\begin{center}
Advisor meeting notes \#X \\
2013-11-11 \\
\end{center}

\begin{table}[H]
\begin{center}
\begin{tabular}{ l | l }
Time and Data & 2013-11-11 14:00 \\
Place & IT building \\
Attendees & Emanuele Di Santo, Sebastian Zalewski \\
Referent & Sebastian Zalewski \\
\end{tabular}
\end{center}
\end{table}

The supervisor has read throught the report.
He thinks that it is good. Content is interesting, language is good.

\textbf{1. Feedback on the report}\newline
-Section 1.2 only have for example name of the customer in title.\\
-Title of section 1.7 “reoprt structure” instead of “summary”.\\
-Move the project tools to the last section of the chapter. (Maybe move to the prestudies).\\
Project management should only contain final tools used (does not need an explanation why).
- Weekly meetings is not so interesting in project manager. It is however possible to keep it
where it is. (Combine with quality assurance, (change name of quality assurance for example management rules))\\
- Functional requirements: give an overview of the whole system. Use natural language to give an
overview how the whole application works together. One paragraph, 3 or 4 sentences how everything works together.\\
- Add a use case diagram for the integration platform as well. Integration platform is not a good name
(in requirement), it doesn’t look like an individual system.\\
- We need to explain why we choose the architecture in the arhictecture chapter.
Constraints. Not highest priority, just to make perfect if we have time. Should contains drivers.\\
- The supervisor wants to add the security chapter into another chapter for example evaluation or prestudies.\\
- Should mention the burndown charts in the text.\\
- Tell something about technical issues, changes in requirements etc. in sprint chapters. A seperate section for it.\\
- Sprint backlog should be moved to the appendix, because it might not be so interesting for the censor.\\
- Too many things in the conclusion. Should cover mainly two parts: the evaluation of the product, and an
evaluation of the process and management.\\
- We should have an evaluation chapter as well as conclusion.\\
- The evaluation: an evaluation how we did it.\\
- Conclusion: summary of the whole report, future work.\\
- The reflection can be simpel (1 or 2 pages) improvement of the course\\
- Should make the headings more descriptive\\

\textbf{2. Questions}\newline
We ask the supervisor what he thinks about the tables. He thinks that all the tables are in
good quality with usefull information. The gant diagram: font might be a bit small (scale it better).
The class diagram should contain alll the classes instead of detailed information of methods and attributes.
Not necceassry to add more to the appendices.
Should explain what JSON is in footnote or something. Not neccessary to add to preliminary studies.

\textbf{3. Delivery}\newline
The customer wants a copy of the report on the 17th for final comments.