% Appendix A - Customer Assignment

\chapter{Assignment for Customer driven project} 

\label{AppendixA}
\lhead{Appendix A. \emph{Assignemnt}}

\textbf{Assignment for Customer driven project}

\textbf{Title:} 	National Integration Platform for Citizen Centric eHealth in Norway \\*
\textbf{Customer (Company):} 	The Directorate of Health, Department of the Health Portal\\*
\textbf{Address:}			Universitetsgata 2, Oslo \\


\textbf{Assignment text:} \\
\textit{Background} \\
The Directorate of Health has a national the task of digitalizing Norwegian healthcare, both by providing coordinated services for specialist healthcare (hospitals) and by providing digital services for citizens in general and patients specifically. 
Examples of such services are ePrescriptions, that is implemented on a national basis, the National Summare Care Record, that will go live in Trondheim in August 2013, and the citizen centric health portal  (helsenorge.no) that has been live since June 2011.

National eHealth projects are complex, long running and costly. There are obvious reasons for this. 
Among these are the complexity and criticality of healthcare, and the scale that national eHealth services represents. 

At the same time, the trends in technology development and consumer adaption of new technology continue to develop. 
Moderate prices and consumer friendly devices that monitor individuals’ health and wellness are increasingly becoming available in the market space. 
Combined with a continuous increase in digital competence in the population, they will influence citizens’ behavior and perspective on their own health situation in the future.

In addition to this, private providers develop great eHealth solutions with consumer and patient orientation. Medhelp.org and Healthvault.com are only two among many examples. 
Ambient assisted living has the potential of revolutionizing life for senior citizens with failing health.

The relevant question is: How can the substantial and long running eHealth projects of the government sector connect to and leverage the dynamics in the market and consumer behavior? 
The answer under investigation is the National Integration Platform (NIP) for Citizen Centric eHealth in Norway. 

\textit{Assignment} \\* 
The assignment is to plan, design and describe a NIP, and to develop a prototype.

The task such a platform should fulfil is to offer interoperability with third party solutions based on available application programmable interfaces (APIs).
All third party solution providers must adhere to specified and standardized rules regarding authentication, security model, messaging and privacy to interact with the NIP. 

The intention of such a platform is to enable the following:
\begin{itemize}
\item Citizens’ ability to publish information they produce from devices in their possession and third party software solutions, including smart phone and tablet apps, into the government run citizen centric health portal (helsenorge.no)
\item Citizens’ ability to fetch information about themselves from helsenorge.no to import it into third party software solutions of their own choosing
\end{itemize}

The assignment is to describe the architecture and major components of the NIP, how it will function on the “outside” regarding third party integration, and on the “inside” regarding integration with helsenorge.no.

It is also essential that the solution adhere to Norwegian privacy regulation and information security. 
Its requirements for integration should also encourage privacy by design within third party solutions.

The prototype should make use of one or more use cases to demonstrate how interaction is performed, how privacy and security concerns are managed and how the end user experience will be. \\


Contact details: 

Name:		Helge T. Blindheim\\
Mobile:		466 75 321\\
E-mail:		helgetb@helsedir.no

